Elephant Seal Age JAE Intraspecific Variation

### 2023-09-18 paper/paper.qmd
Suppressed messages and code
Add citations

---
title: "Elephant Seal Age JAE Intraspecific Variation"
format: html
editor: visual
---

```{r}
#| label: setup

@@

>>>>

---
title: "Elephant Seal Age JAE Intraspecific Variation"
format: 
  html: 
    echo: false 
editor: visual
bibliography: references.bib
---

```{r}
#| label: setup
#| include: false

@@

This paper is basically the same as another paper about polar bears (*Ursus maritimus*) [@naciri2022].
